\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{amsmath}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Matthew Pace}
\address{Barrington, Cambridgeshire}

\address{
\textcolor{blue}{\href{https://www.linkedin.com/in/matthewpace98/}{LinkedIn}} \\ 
\textcolor{blue}{\href{https://github.com/MatthewPace98}{Github}} \\
\textcolor{blue}{\href{https://MaltiOmics.com}{Website}}
}

\address{+44~$\cdot$~77787~$\cdot$~40848 \\ \href{mailto:matthew.pobox@gmail.com}{matthew.pobox@gmail.com }}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{rSection}{Summary}
Bioinformatician with four years experience, currently working  as the sole computational biologist in a gene therapy start-up. Built the company's analytical infrastructure from scratch using Nextflow, and adapted it to the company's rapidly changing needs. Skilled in machine learning, cloud computing, and next-generation sequencing analysis.
\end{rSection}


\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, Bash, R \\
Web Technology & Flask, Shiny, HTML, CSS, JavaScript \\
Sequencing & NGS, scRNA-Seq, WGS \\
Cloud Computing & Amazon Web Services \\ \\
\end{tabular}
\end{rSection}

\begin{rSection}{Experience}
\begin{rSubsection}{
 Research Associate, OrthoBio Therapeutics}
{November 2022 - Present}{CRUK-CI, Cambridge, UK}{ }
\item Lead the bioinformatics component in a start-up utilising genetic knock-outs to reduce synovial inflammation.
\item Managed our AWS account for data archival in S3 buckets and launched optimised EC2 compute instances.
\item Developed a pan-species guide RNA performance prediction pipeline utilising machine learning models to rank spacer sequences by predicted efficacy and specificity.
\item Compiled a statistical report of our canine preclinical trial for FDA review, testing therapeutic efficacy using a linear mixed-effects model.
\item Automated an Amp-Seq data analysis pipeline using Nextflow to output on- and off-target gene edit percentages from raw Illumina sequencing data.
\item Analysed single-cell RNA-Seq data from online repositories to identify key target nodes to knock out.
\item Performed bulk RNA-Seq analysis to observe the downstream effects of gene knock-outs \textit{in vitro}.
\item Generated protein structure prediction models with AlphaFold2 to optimise a novel CRISPR-Cas9 nuclease for nuclear localisation signal binding.
\item Fine-tuned the Geneformer transformer model with osteoarthritic scRNA-Seq data to predict key gene knock-out targets for restoring tissue health.
\item Presented results to our American team of clinicians, lawyers, and financial officers during our weekly meetings.
\item Used output from aforementioned pipelines to generate evidence supporting eight patents filed by the company.
\end{rSubsection}

\begin{rSubsection}{
Research Support Officer I, TargetID {\href{https://www.um.edu.mt/projects/targetid}{\textcolor{blue}{\ExternalLink} }}}
{March 2021 - June 2022}{University of Malta, Malta}{ }
\item Co-developed a Flask-based API for user-friendly filtering on our gene variant database.
\item Routinely interacted with terabytes of data hosted on our server cluster through the Slurm Workload Manager.
\item Performed quantitative analysis on survey results to search for correlations between lifestyle and gene expression.
\item Archived genomic data from over 1000 patients on our Google Cloud Platform.
\item Benchmarked genomic file compressors and identified the optimal tools for data archiving, reducing storage requirements by 74\%.
\end{rSubsection}

%\begin{rSubsection}{
%Presenter, Malta National Aquarium}
%{July 2017 - June 2020}{St. Paul's Bay, Malta}{ }
%\item Part-time job which involved giving informative talks to %customers about the present aquatic species.
%\end{rSubsection}
\end{rSection}
\pagebreak

\begin{rSection}{Education}
\begin{rSubsection}{Master of Science in Bioinformatics}{October 2020 - July 2022}{University of Malta, Malta}{ }
\item Taught component included \textit{inter alia} HTS methods, managing relational databases with SQL, the use of Python and the Linux command line, and statistics using R.
\item Dissertation: "RNA-seq Analysis of an Acute Myeloid Leukaemia Cell Line Treated with Phenolic Compounds".
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Bachelor of Science (Hons) in Biology}{October 2017 - June 2020}{University of Malta, Malta}{ }
\item Provided theoretical and practical experience across all major branches of biology including \textit{inter alia} genetics, biotechnology, and ecology.
\item Dissertation: "Quantitative Analysis of Bottom Otter Trawl Discards in the Strait of Sicily".
\end{rSubsection}
\end{rSection}

\begin{rSection}{Completed Courses}
\begin{table}[h!]
\begin{tabular}{@{}>{}l@{\hspace{6ex}}l@{\hspace{6ex}}c@{}}
Linear modeling: Hands-on with Fixed and Mixed Effects & University of Cambridge & March 2025 \\
Introduction to Single-cell RNA-seq Data Analysis \href{https://www.linkedin.com/in/matthewpace98/overlay/1635545693672/single-media-viewer/?profileId=ACoAACS_U8EBVhdDUy9KmRe-0zhttQScplbaMnk}{\textcolor{blue}{\ExternalLink}} & University of Cambridge & September 2023 \\
Artificial Intelligence Foundations: Machine Learning \href{https://www.linkedin.com/learning/certificates/ff5dd95dae7cc4d94f6d8bd890764ca89388773d610c4b9ff39d080adb383d36}{\textcolor{blue}{\ExternalLink}} & LinkedIn & July 2023
\end{tabular}
\end{table}
\end{rSection}

\begin{rSection}{Pending Publication}
\begin{itemize}[leftmargin=1pt]

\item Borg Carbott, F., Vella, M., Borg, J., Portelli, C., Attard, R., Dingli, P., Vassallo, J., \textbf{Pace, M.}, Cassar, K., Ebejer, J.P., Formosa, M.M., Farrugia, R., Bezzina Wettinger, S. \textit{Clinical Applications of a Whole Genome Sequencing Study: Examples From Malta, a Mediterranean Population}. European Journal of Human Genetics (submitted), 2025. 

\textbf{Contribution}: Optimisation of NGS data analysis pipelines, data collection, and data archival.
\end{itemize}
\end{rSection}

\begin{rSection}{IP Contributions}
\begin{itemize}[leftmargin=1pt]

\item \textit{Lipid Nanoparticles for Gene Editing Systems}\\WO 2024/215959

\item \textit{Gene Editing to Improve Joint Function}\\WO 2023/147442, WO 2023/288135, WO 2022/016121

\item \textit{Gene Editing for Surgery-Related Fibrosis Treatment}\\WO 2024/155948

\item \textit{Transmembrane Receptor Gene Editing}\\WO 2023/141531

\item \textit{Gene Editing for Intervertebral, Intra- and Peridiscal Therapy and Associated Spinal Disorders}\\WO 2024/215956, WO 2023/201269 
\end{itemize}
\end{rSection}

\begin{rSection}{Miscellaneous}
\begin{itemize}[leftmargin=1pt]

\item Ranked $28^{\text{th}}$ out of 2190 applicants in Malta's Common Entrance Examination.
\item Coauthored a local news article{\href{https://timesofmalta.com/article/understanding-bioinformatics-the-key-to-unlocking-our-genetic-secrets.948217}{\textcolor{blue}{\ExternalLink}}} promoting bioinformatics.
\end{itemize}

\end{rSection}
\end{document}
